Technical Report

### 2017-11-07 fully-abstract-comp/technical-report.tex
added address stratified definition
added the 'normal' capabilities to the value relation
Typo.
typo.
renamed regions (pure to spatial, normal to pure)

\newcommand{\World}{\mathrm{World}}
\newcommand{\RegionName}{\mathrm{RegionName}}
\newcommand{\Region}{\mathrm{Region}}
\newcommand{\pure}{\mathrm{pure}}
\newcommand{\pureo}{\mathrm{pure\_owned}}
\newcommand{\normReg}{\mathrm{normal}}
\newcommand{\State}{\mathrm{State}}
\newcommand{\Rels}{\mathrm{Rels}}
\newcommand{\UPred}[1]{\mathrm(#1)}

@@

\section{Logical Relation}
\subsection{Worlds}
\lau{30-10-2017: TODO: solve recursiveness in domain equation in the following. }
\lau{02-11-2017: We may need revoked regions again to handle the stack.}
\lau{06-11-2017: If we need to introduce revoked regions like we hade for the local capabilities, we may consider the following: For the future world relation require the existance of a bijection from region names to region names. For all regions in the present world the future region is given by the bijection. This would mean that reinstantiation would happen simply by giving a bijection that maps to the new region. In other words, the weird shadowing would not be necessary.
  \begin{mathpar}
    \inferrule{ \dom(W') \supseteq \dom(W) \\ \exists m : \RegionName \fun \RegionName, \text{ $m$ injective} \ldotp \forall r \in \dom(W) \ldotp W'(m(r)) \pubft W(r) }
    { W' \pubft W }
  \end{mathpar}
}
\[
  \World = \RegionName \parfun \Region
\]
where $\RegionName = \nats$.
\[
  \Region = \left\{
  \begin{array}{l}
    \{\pure \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\pureo \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\normReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})
  \end{array} \right.
\]
where $\pure$ and $\pureo$ are regions governing segments of memory addressed by linear capabilities. $\pureo$ signifies that this region is addressable. $\pure$ signifies that the region is not owned and can thus not be addressed. Finally, $\normReg$ signifies that the region is only addressed by non-linear capabilities. Notice that no region allows for both linear and non-linear capabilities to address it.
\lau{26-20-2017: We may also want to build the infrastructure for the stack more explicitely into the worlds (but maybe we can handle it in the memory satisfaction).}
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}
  \[
   \Rels = \{\phi_\pub \times \phi \in \powerset{\State^2}\times \powerset{\State^2} \mid \phi_\pub, \phi \text{ is reflexive and transitive and } \phi_\pub \subseteq \phi \}
  \]

Disjoint union of worlds. Joins together two alike worlds with strictly disjoint ownership over $\pureo$-regions.
\[
  W_1 \oplus W_1 = W
  \begin{array}[t]{l}
    \text{if $\dom(W) = \dom(W_1) = \dom(W_2) \tand$} \\
    \forall r \in \dom(W) \ldotp W(r) = W_1(r) \oplus W_2(r)
  \end{array}
\]
$\oplus$ is defined as follows
\begin{align*}
  (\normReg,\var{sm}) \oplus (\normReg,\var{sm}) =  & \; (\normReg,\var{sm}) \\
  (\pureo,\var{sm}) \oplus (\pure,\var{sm}) = & \; (\pure,\var{sm}) \oplus (\pureo,\var{sm})\\
                                           =  & \; (\pureo,\var{sm}) \\
  (\pure,\var{sm}) \oplus (\pure,\var{sm}) =  & \; (\pure,\var{sm}) \\
\end{align*}
and for all other cases $\oplus$ is undefined. Specifically, $\oplus$ is not defined when both sides are a $\pureo$-region. It is further not defined if the two sides do not agree on region type and state machine. Here $\var{sm}$ is the state machine of the region.

@@

\subsection{Memory satisfaction}
\[
  \memSat{\ms_S,\ms_\stk,\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      \exists R_\ms : \dom(W) \fun \MemSeg^2 \ldotp \\
      \quad \ms_T = \biguplus_{r \in \dom(W)} \pi_2(R_\ms(r)) \wedge \\
      \quad \stk = (\_,\ms_{\stk,0}) :: \dots :: (\_,\ms_{\stk,m}) \wedge \\
      \quad \exists r_0 , \dots, r_m, r_{m+1} \ldotp \pi_1(R_\ms(r_0,\dots,r_m)) = \ms_{\stk,0},\dots , \ms_{\stk,m} \wedge \\
      \qquad \pi_1(R_\ms(r_{m+1})) = \ms_\stk \wedge \\
      \qquad \ms_S \uplus \ms_\stk \uplus \ms_{\stk,0} \uplus \dots \ms_{\stk,m} = \biguplus_{r \in \dom(W)} \pi_1(R_\ms(r)) \wedge \\
      \qquad \exists R_w : \dom(W) \fun \World \ldotp\\
      \quad \qquad W = \biguplus_{r \in \dom(W)} R_w(r) \wedge \\
      \quad \qquad \forall r \in \dom(W) , n' < n \ldotp \\
      \qquad \qquad \npair[n']{R_\ms(r)} \in W(r).H \; (W(r).s) \; (\xi^{-1} (R_w (r))) 
    \end{array}
  \right.
\]
In the definition of memory satisfaction, $R_\ms$ acts as a partitioning in the two related memories. As the source language is a special interpretation of the target language, part of the target memory needs to relate to the stack in the source language. We also need to split up the world which is done by $R_W$.We split up the world in order to make sure that the linearity constraints impossed by the world are satisfied.
\lau{30-10-2017: It is not clear to me whether this definition should also talk about $\opc$.}

\subsection{Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\lau{19-10-2017: Maybe linearity should be taken care of in just one place (instead of in $\lrr$ relation and mem staisfaction). That is, add a predicate that checks whether the configuration satisfies linearity (such a condition may be to syntactic to work?).}
In the following definitions, \src{blue} is used to indicate values related to the source machine. This is unlike previous definitions, where \src{blue} is used  indicate source language specific parts of definitions.
\[
  \lre(W) = \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{k_{d,S}}, \src{k_{c,S}}, k_{d,T}, k_{c,T}, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrk, W_\lrr, W_\lrm \ldotp \\
      \qquad\npair[n']{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair[.]{k_{d,S},k_{c,S}}{k_{d,T},k_{c,T}}} \in \lrk(W_\lrk) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Rightarrow\\
      \qquad\npair[n']{\left(\array{l}\src{(\ms_S,\reg_S\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,S},v_{d,S},k_{c,S},k_{d,S}},\stk, \ms_\stk)},\\
                                          (\ms_T,\reg_T\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,T},v_{d
,T},k_{c,T},k_{d,T}})\endarray\right)}
      \in \lro(W\oplus W_\lrk \oplus W_\lrr \oplus W_\lrm)
    \end{array}
    \right\}
\]
\lau{24-10-2017: Dominique, I do not see how the splitting of worlds is going to work out. I can see how it will enforce linearity, but is you give a "pure" region (the kind of region that is only allowed to go to one part of a split) to the $\lrr$-relation, then the memory satisfation does not have it, and it cannot find a memory segment for this part. In other words, the memory satisfaction will not be able to find a concrete memory segment for segments governed by a linear capability in the register file. Maybe the memory satisfaction should have all of the parts, so it can represent them (but also limit what linear capabilities can be used).}

@@

\[
  \lrr(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : \RegName \fun \World \ldotp \\
      \quad S \text{ is a separation of $W$} \tand\\
      \quad \forall r \in \RegName \setminus \{\pcreg, \rretd,\rretc \}\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
Where $S\text{ is a separation of $W$}$ means that no two partion share the same ``pure'' region (whatever that is).

\[
  \lrv(W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \middle| i \in \ints \right\}\cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrc(\sigma,\_)},\\\sealed{\sigma,\vsc_C}\endarray\right)} \middle| 
    \begin{array}{l}
    \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrd(\sigma,\_)}{\sealed{\sigma,\vsc_D}}} \in \lrv(W_\lrv) \ldotp\\
      \npair[n']{\retptrc(\sigma,\_),\retptrd(\sigma,\_),\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \oplus W_\lrv)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrd(\sigma,\_)},\\\sealed{\sigma,\vsc_D}\endarray\right)} \middle| 
    \begin{array}{l}
    \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrc(\sigma,\_)}{\sealed{\sigma,\vsc_C}}} \in \lrv(W_\lrv) \ldotp\\
      \npair[n']{\src{\retptrc(\sigma,\_)},\src{\retptrd(\sigma,\_)},\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \oplus W_\lrv)
    \end{array}
    \right\}\cup \\
    \left\{ \npair{\left(\array{l}\src{\sealed{\sigma,\vsc_S}},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \middle|
    \begin{array}{l}

    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \middle|
    \right\}
  \end{array}
\]

\subsection{Permission based conditions}
\[
  \addressable{\lin,W} =
  \begin{cases}
    \{ r \mid W(r) = (\normal,\_) \} & \text{if $\lin = \normal$} \\
    \{ r \mid W(r) = (\pureo,\_) \}  & \text{otherwise (i.e. $\lin = \linear$)} \\
  \end{cases}
\]

@@

\lau{01-11-2017: TODO Write down address-stratified condition.}

>>>>

\newcommand{\World}{\mathrm{World}}
\newcommand{\RegionName}{\mathrm{RegionName}}
\newcommand{\Region}{\mathrm{Region}}
\newcommand{\spatial}{\mathrm{spatial}}
\newcommand{\spatialo}{\mathrm{spatial\_owned}}
\newcommand{\pure}{\mathrm{pure}}
\newcommand{\State}{\mathrm{State}}
\newcommand{\Rels}{\mathrm{Rels}}
\newcommand{\UPred}[1]{\mathrm(#1)}

@@

\section{Logical Relation}
\subsection{Worlds}
\lau{30-10-2017: TODO: solve recursiveness in domain equation in the following. }
\lau{02-11-2017: We may need revoked regions again to handle the stack.}
\lau{06-11-2017: If we need to introduce revoked regions like we hade for the local capabilities, we may consider the following: For the future world relation require the existance of a bijection from region names to region names. For all regions in the present world the future region is given by the bijection. This would mean that reinstantiation would happen simply by giving a bijection that maps to the new region. In other words, the weird shadowing would not be necessary.
  \begin{mathpar}
    \inferrule{ \dom(W') \supseteq \dom(W) \\ \exists m : \RegionName \fun \RegionName, \text{ $m$ injective} \ldotp \forall r \in \dom(W) \ldotp W'(m(r)) \pubft W(r) }
    { W' \pubft W }
  \end{mathpar}
}
\[
  \World = \RegionName \parfun \Region
\]
where $\RegionName = \nats$.
\[
  \Region = \left\{
  \begin{array}{l}
    \{\spatial \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\spatialo \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\pure \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})
  \end{array} \right.
\]
where $\spatial$ and $\spatialo$ are regions governing segments of memory addressed by linear capabilities. $\spatialo$ signifies that this region is addressable. $\spatial$ signifies that the region is not owned and can thus not be addressed. Finally, $\pure$ signifies that the region is only addressed by non-linear capabilities. Notice that no region allows for both linear and non-linear capabilities to address it.
\lau{26-20-2017: We may also want to build the infrastructure for the stack more explicitely into the worlds (but maybe we can handle it in the memory satisfaction).}
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}
  \[
   \Rels = \{\phi_\pub \times \phi \in \powerset{\State^2}\times \powerset{\State^2} \mid \phi_\pub, \phi \text{ is reflexive and transitive and } \phi_\pub \subseteq \phi \}
  \]

Disjoint union of worlds. Joins together two alike worlds with strictly disjoint ownership over $\spatialo$-regions.
\[
  W_1 \oplus W_1 = W
  \begin{array}[t]{l}
    \text{if $\dom(W) = \dom(W_1) = \dom(W_2) \tand$} \\
    \forall r \in \dom(W) \ldotp W(r) = W_1(r) \oplus W_2(r)
  \end{array}
\]
$\oplus$ is defined as follows
\begin{align*}
  (\pure,\var{sm}) \oplus (\pure,\var{sm}) =  & \; (\pure,\var{sm}) \\
  (\spatialo,\var{sm}) \oplus (\spatial,\var{sm}) = & \; (\spatial,\var{sm}) \oplus (\spatialo,\var{sm})\\
                                           =  & \; (\spatialo,\var{sm}) \\
  (\spatial,\var{sm}) \oplus (\spatial,\var{sm}) =  & \; (\spatial,\var{sm}) \\
\end{align*}
and for all other cases $\oplus$ is undefined. Specifically, $\oplus$ is not defined when both sides are a $\spatialo$-region. It is further not defined if the two sides do not agree on region type and state machine. Here $\var{sm}$ is the state machine of the region.

@@

\subsection{Memory satisfaction}
\[
  \memSat{\ms_S,\ms_\stk,\stk,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      \exists R_\ms : \dom(W) \fun \MemSeg^2 \ldotp \\
      \quad \ms_T = \biguplus_{r \in \dom(W)} \pi_2(R_\ms(r)) \wedge \\
      \quad \stk = (\_,\ms_{\stk,0}) :: \dots :: (\_,\ms_{\stk,m}) \wedge \\
      \quad \exists r_0 , \dots, r_m, r_{m+1} \ldotp \pi_1(R_\ms(r_0,\dots,r_m)) = \ms_{\stk,0},\dots , \ms_{\stk,m} \wedge \\
      \qquad \pi_1(R_\ms(r_{m+1})) = \ms_\stk \wedge \\
      \qquad \ms_S \uplus \ms_\stk \uplus \ms_{\stk,0} \uplus \dots \ms_{\stk,m} = \biguplus_{r \in \dom(W)} \pi_1(R_\ms(r)) \wedge \\
      \qquad \exists R_w : \dom(W) \fun \World \ldotp\\
      \quad \qquad W = \bigoplus_{r \in \dom(W)} R_w(r) \wedge \\
      \quad \qquad \forall r \in \dom(W) , n' < n \ldotp \\
      \qquad \qquad \npair[n']{R_\ms(r)} \in W(r).H \; (W(r).s) \; (\xi^{-1} (R_w (r))) 
    \end{array}
  \right.
\]
In the definition of memory satisfaction, $R_\ms$ acts as a partitioning in the two related memories. As the source language is a special interpretation of the target language, part of the target memory needs to relate to the stack in the source language. We also need to split up the world which is done by $R_W$.We split up the world in order to make sure that the linearity constraints impossed by the world are satisfied.
\lau{30-10-2017: It is not clear to me whether this definition should also talk about $\opc$.}

\subsection{Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\lau{19-10-2017: Maybe linearity should be taken care of in just one place (instead of in $\lrr$ relation and mem staisfaction). That is, add a predicate that checks whether the configuration satisfies linearity (such a condition may be to syntactic to work?).}
In the following definitions, \src{blue} is used to indicate values related to the source machine. This is unlike previous definitions, where \src{blue} is used  indicate source language specific parts of definitions.
\[
  \lre(W) = \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{k_{d,S}}, \src{k_{c,S}}, k_{d,T}, k_{c,T}, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrk, W_\lrr, W_\lrm \ldotp \\
      \qquad\npair[n']{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair[.]{k_{d,S},k_{c,S}}{k_{d,T},k_{c,T}}} \in \lrk(W_\lrk) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Rightarrow\\
      \qquad\npair[n']{\left(\array{l}\src{(\ms_S,\reg_S\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,S},v_{d,S},k_{c,S},k_{d,S}},\stk, \ms_\stk)},\\
                                          (\ms_T,\reg_T\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,T},v_{d
,T},k_{c,T},k_{d,T}})\endarray\right)}
      \in \lro(W\oplus W_\lrk \oplus W_\lrr \oplus W_\lrm)
    \end{array}
    \right\}
\]
\lau{24-10-2017: Dominique, I do not see how the splitting of worlds is going to work out. I can see how it will enforce linearity, but is you give a "spatial" region (the kind of region that is only allowed to go to one part of a split) to the $\lrr$-relation, then the memory satisfation does not have it, and it cannot find a memory segment for this part. In other words, the memory satisfaction will not be able to find a concrete memory segment for segments governed by a linear capability in the register file. Maybe the memory satisfaction should have all of the parts, so it can represent them (but also limit what linear capabilities can be used).}

@@

\[
  \lrr(W) = \left\{ \npair{\stpair{\reg}{\reg}} \middle|
    \begin{array}{l}
      \exists S : \RegName \fun \World \ldotp \\
      \quad S \text{ is a separation of $W$} \tand\\
      \quad \forall r \in \RegName \setminus \{\pcreg, \rretd,\rretc \}\ldotp\\
      \qquad\npair{\stpair[.]{\src{\reg_S(r)}}{\reg_T(r)}} \in \lrv(S(r))
    \end{array}
            \right\}
\]
Where $S\text{ is a separation of $W$}$ means that no two partion share the same ``spatial'' region (whatever that is).

\[
  \lrv(W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrc(\sigma,\_)},\\\sealed{\sigma,\vsc_C}\endarray\right)} \;\middle| \;
    \begin{array}{l}
    \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrd(\sigma,\_)}{\sealed{\sigma,\vsc_D}}} \in \lrv(W_\lrv) \ldotp\\
      \npair[n']{\retptrc(\sigma,\_),\retptrd(\sigma,\_),\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \oplus W_\lrv)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrd(\sigma,\_)},\\\sealed{\sigma,\vsc_D}\endarray\right)} \;\middle| \;
    \begin{array}{l}
    \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrc(\sigma,\_)}{\sealed{\sigma,\vsc_C}}} \in \lrv(W_\lrv) \ldotp\\
      \npair[n']{\src{\retptrc(\sigma,\_)},\src{\retptrd(\sigma,\_)},\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \oplus W_\lrv)
    \end{array}
    \right\}\cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\sealed{\sigma,\vsc_S}},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}

    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} \;\middle|\;
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{r l l }
      \perm \in \readAllowed{} &\Rightarrow& \npair{\baddr,\eaddr} \in \readCond{\lin,W}\\
      \perm \in \writeAllowed{} &\Rightarrow& \npair{\baddr,\eaddr} \in \writeCond{\lin,W}\\
      \perm = \rwx &\Rightarrow& \npair{\{\rwx,\rx\},\baddr,\eaddr} \in \execCond{\lin,W}\\
      \perm = \rx &\Rightarrow& \npair{\{\rx\},\baddr,\eaddr} \in \execCond{\lin,W}
    \end{array}

    \right\}
  \end{array}
\]

\subsection{Permission based conditions}
\[
  \addressable{\lin,W} =
  \begin{cases}
    \{ r \mid W(r) = (\normal,\_) \} & \text{if $\lin = \normal$} \\
    \{ r \mid W(r) = (\spatialo,\_) \}  & \text{otherwise (i.e. $\lin = \linear$)} \\
  \end{cases}
\]

@@

\begin{definition}
  \label{def:address-stratified}
  We say that a region $\iota = (\_,\_,\_,\_,H)$ is address stratified iff
  \[
    \begin{array}{l}
      \forall n, \src{\ms_S},\ms_T,\src{\ms_S'},\ms_T',s,\hat{W}\ldotp \\
      \quad \npair{\stpair{\ms}{\ms}}, \npair{\stpair[.]{\ms_S'}{\ms_T'}} \in H \; s \; \hat{W} \wedge \\
      \quad \dom(\src{\ms_S}) = \dom(\ms_T) = \dom(\src{\ms_S'}) = \dom(\ms_T') \\
      \quad \Rightarrow \\
      \qquad \forall \aaddr \in \dom(\ms_S) \ldotp \npair{(\src{\ms_S}\update{\aaddr}{\src{\ms_S'}(\aaddr)},\ms_T\update{\aaddr}{\ms_T'(\aaddr)})} \in H \; s \; \hat{W}
    \end{array}
  \]
\end{definition}
